Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-26 Scripts/Initial_Analysis.Rmd
Changes to functions

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
       model = "GFDL",
      rcp = "85",
      path = "NA",
      my_path = F
    )
  )

@@

mclapply(
  spp_list,
  EstPropChange,
  year <- year_df$year,
  data_type <- "Catch",
  ensemble_list = ensemble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

@@

# Hall 1000 ran it in 5.33 hours

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensemble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x) %>% 
        # Estimate distances between spp centroid and EEZ centroid
        mutate(
          distance = geodist(longitude, # eez longitude
                             latitude,  # eez latitude
                             lon,  # species longitude
                             lat, # species latitude
                             units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensemble,year,distance)

@@

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensemble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup() %>% 
    mutate(value = ifelse(is.na(value),0,value)) %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_")
    )
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    # )
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>%
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

  # Average of 10 years mean of ensemble members results
  mean_sd_index <- Trans_index %>% 
    group_by(taxon_key,year,neighbour_id) %>% 
    summarise_at(vars("RMean"),
                 c(trend=mean,
                   ensemble_sd=sd,
                   n_ens = ~n())
    )

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year < Hist_y) %>% 
    group_by(taxon_key) %>% 
    summarise_at(vars("RMean"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
    )

  # For testing
  if(Plot == T){
  # Plot the result, bruh

@@

  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    # Conditional, will only plot circles if the data exists
    {if(Plot_Test)geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    )
      } +
    geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +
    ggsave(paste(taxon_key,Id,"plot_example.jpg",sep="_"),
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R")
       )

@@

    Final_Result <- mean_sd_index %>%
      group_by(taxon_key,neighbour_id,n_ens) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr)

@@

  # Identifies the year of emergence (e.g. trend > noise)
  Final_Result <- mean_sd_index %>%
    filter(year > Hist_y,
           trend > (historic_sd$hist_mean+historic_sd$noise) |
             trend < (historic_sd$hist_mean-historic_sd$noise)
    ) %>%
    group_by(taxon_key,neighbour_id,n_ens) %>%
    summarise(emerging_yr= min(year)) %>%
    left_join(EEZ_ids,
              by = "neighbour_id") %>%
    ungroup() %>%
    select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr)

@@

GetTransIndex <- function(taxon_key,
                          year,
                          Hist_y,
                          data_type = "Catch",
                          path,
                          ensemble_list,
                          Neighbours,
                          eez_centroid){
  t_start <- Sys.time()
  print("Starting Step One")
    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

    name <- paste(my_path("R",extra_path = "/Emergence/"),taxon_key,"_emergence.txt",sep="")

@@

@@

    Emerging_result <- bind_rows(
      lapply(spp_reman[63],
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Catch",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )

@@

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion_2005/"),"proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean, na.rm = T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))
    }

@@

   eez_summary <- spp %>% 
     group_by(eez_name,eez_neighbour,time_step) %>% 
     summarise(
       n_spp = n(),
       min_eez = min(mean_spp, na.rm=T),
       max_eez = max(mean_spp, na.rm=T),
       sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_eez = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_eez,mean_eez,sd_eez)

@@

   eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
       n_spp = n(),
       min_eez = min(mean_spp, na.rm=T),
       max_eez = max(mean_spp, na.rm=T),
       sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_eez = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_eez,mean_eez,sd_eez)

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_eez) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_early" = early,
     "per_mid" = mid
     ),
            funs(round((((.-historical)/historical))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Proportion_2005",sep=""))

@@

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  filter(!is.na(eez_neighbour)) %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           ),
         per_early_plot =ifelse(per_early >= 50, 50,
                           ifelse(per_early <= -50,-50,per_early)
                           )
         )

# For dat availabillity
 # write_csv(results,
          # "proportion_change_2005.csv")

@@

# The path
path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early_plot),0,per_early_plot),
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_eez"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_mid_plot:per_early_plot)

@@

Data <- Data %>% 
  gather("time_step","per_chng",per_mid_plot:per_early_plot)

gc()# clean ram

# time <- "per_mid_plot"
time <- "per_early_plot"

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    direction = -1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

##### Histogram of change

```{r hist_change}

 results %>% 
  gather("time_step","change",per_early,per_mid) %>% 
  filter(variable == "mean_eez" & 
           !is.na(change)
         ) %>%
ggplot() +
  geom_density(
               aes(
                 x = ifelse(change >= 100,100,change),
                 # x = change,
                 fill = ifelse(time_step == "per_early","q",time_step)
                 # fill = time_step,

               ),
               # stat = "count",
               # alpha= 0.8,
               size=0.1,
               # position = "stack"
  ) +
  scale_y_continuous("Density",
                     # breaks = seq(0,90,10),
                     # limits = c(0,100)
  ) +
  scale_x_continuous("Percentage Change",
                     breaks = seq(-75,500,25)
  ) +
  my_ggtheme_p() +
  theme(legend.position = "right") +
  scale_fill_viridis(discrete = T, 
                     option = "plasma",
                     alpha = 0.5,
                     name = "Time Step", labels = c("Middle", "Early")
                     ) +
  coord_flip() +
  ggsave("./Figures/hist_change.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

# Get taxon list
Taxon_List <- list.files(my_path("R",extra_path = "Emergence_2005"))

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List,"_emergence.txt",sep="")

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  )
# warnings() for empty data species

@@

# Per Stock
stock_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,taxon_key,Tresh) %>%
  # summarise(n_tax = length(unique(eez_name))) %>%
  summarise(n()) %>% 
  mutate(
    level = "stock"
  ) 
  # ggplot() +
  # geom_histogram(
  #   aes(
  #     x = emerging_yr
  #   ),
  #   stat = "count"
  # )

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eez_name,emerging_yr,Tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  ungroup() %>% 
  select(1,3,4)

hist_data <- stock_d_hist %>% 
  bind_rows(eez_d_hist) %>% 
  filter(Tresh != "NA")

ggplot() +
  geom_density(data = subset(hist_data, level == "EEZ"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
  geom_density(data = subset(hist_data, level == "stock"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
    scale_y_continuous("Frequency",
                       breaks = seq(0,90,10),
                       limits = c(0,100)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  facet_wrap(~Tresh)

@@

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key,Tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,Tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  ) %>% 
    select(1,3,4)

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(eez_name,Tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,Tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  ) %>% 
    select(1,3,4)

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(Tresh != "NA")

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    # Comment out for option A (Change plot name!!)
    geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
    geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,500,50),
                       limits = c(0,500)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
    facet_wrap(~Tresh)
  # ggsave("./Figures/figure_accumulative_curve_B.png",
  #        width = 6,
  #        height = 6,
  #        units = "in"
  # )
```

>>>>

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      model = "GFDL",
      rcp = "85",
      # path = "/Volumes/DATA/DATA",
      my_path = F
    )
  )

@@

mclapply(
  spp_list,
  EstPropChange,
  year = year_df$year,
  data_type = "Catch",
  ensemble_list = ensemble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

@@

# Hall 1000 ran it in 5.33 hours past
# Hall 1000 ran it in  hours (July 2020)

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensemble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x) %>% 
        # Estimate distances between spp centroid and EEZ centroid
        mutate(
          distance = geodist(latitude,  # eez latitude
                             longitude, # eez longitude
                             lat, # species latitude
                             lon,  # species longitude
                             units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensemble,year,distance)

@@

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensemble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup() %>% 
    mutate(value = ifelse(is.na(value),0,value)) %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_")
    )
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    # )
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    # filter(year > 1960) %>%
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

  # Average of 10 years mean of ensemble members results
  mean_sd_index <- Trans_index %>% 
    group_by(taxon_key,year,neighbour_id) %>% 
    summarise_at(vars("RMean"),
                 c(trend=mean,
                   ensemble_sd=sd,
                   n_ens = ~n()
    )
    )

    # Valid ensembles
  # Only perform analysis on ensembles containing all years between 1951 and 2040
    n_years <- mean_sd_index %>% 
      group_by(n_ens) %>% 
      summarise(
        n_year = n()
      ) %>% 
      filter(
        n_year == 149
      )

    mean_sd_index <- mean_sd_index %>% 
      filter(n_ens %in% n_years$n_ens)

  # Estimate noice from ensemble members
  historic_sd <- mean_sd_index %>% 
    filter(year <= Hist_y,
           n_ens %in% n_years$n_ens) %>% 
    group_by(taxon_key,neighbour_id) %>% 
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
    )

  # For testing
  if(Plot == T & length(historic_sd$hist_mean) > 1){
  # Plot the result, bruh

@@

  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-(historic_sd$noise*2),
                    ymax=historic_sd$hist_mean+(historic_sd$noise)*2)
                ,
                alpha = 0.5,
                fill = "grey30"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    # Conditional, will only plot circles if the data exists
    {if(Plot_Test)geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    )
      } +
    geom_vline(xintercept = Hist_y,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +

    tk <- unique(mean_sd_index$taxon_key)

    ggsave(paste(tk,Id,"plot_example.jpg",sep="_"),
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R")
       )

@@

    Final_Result <- mean_sd_index %>%
      group_by(taxon_key,neighbour_id,n_ens) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr) %>% 
      mutate(Tresh= NA)

@@

  Final_Result <- mean_sd_index %>%
    filter(year > Hist_y) %>% 
    mutate(
           Tresh_one = ifelse(trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise),"One",NA),
           Tresh_two = ifelse(trend > (historic_sd$hist_mean+(2*historic_sd$noise)) | trend < (historic_sd$hist_mean-(2*historic_sd$noise)),"Two",NA)
    ) %>%
    gather("Tresh","YesNo",Tresh_one,Tresh_two) %>% 
    filter(!is.na(YesNo)) %>% 
    group_by(taxon_key,neighbour_id,n_ens,Tresh) %>%
    summarise(emerging_yr= min(year)) %>%
    left_join(EEZ_ids,
              by = "neighbour_id") %>%
    ungroup() %>%
    select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr,Tresh)

@@

GetTransIndex <- function(taxon_key,
                          year,
                          Hist_y,
                          data_type = "Catch",
                          path,
                          ensemble_list,
                          Neighbours,
                          eez_centroid,
                          Plot = F){
  t_start <- Sys.time()
  print("Starting Step One")
    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

    name <- paste(my_path("R",extra_path = "/Emergence_2005/"),taxon_key,"_emergence.txt",sep="")

@@

rand_plot <- sample(spp_reman,5)

@@

gc()

    Emerging_result <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Abd",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid,
               Plot = F
      )
    )

@@

  # Reads taxon data
  proportion_data <- fread(paste(result_path,"Proportion/","proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )
    }

@@

   eez_summary <- spp %>% 
     group_by(eez_name,eez_neighbour,time_step) %>% 
     summarise(
       n_spp = n(),
       min_spp = min(mean_spp,na.rm=T),
       max_spp = max(mean_spp,na.rm=T),
       sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_spp = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_spp,mean_spp,sd_spp)

@@

   eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
     n_spp = n(),
     min_spp = min(mean_spp,na.rm=T),
     max_spp = max(mean_spp,na.rm=T),
     sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
     mean_spp = mean(mean_spp,na.rm=T)
   ) %>% 
   select(eez_name:max_spp,mean_spp,sd_spp)

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/.))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Propotion",sep=""))

@@

# Run results
Proportion_Results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid =ifelse(per_mid >= 25, 25,
                           ifelse(per_mid <= -25,-25,per_mid)
                           )
         )

@@

# The path
path_world <- paste(data_path,"Spatial/SAU_Shapefile/",sep="")

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

@@

gc()# clean ram
x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,25),
    breaks = seq(0,25,5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connectionsc.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

# Get taxon list
Taxon_List <- list.files(my_path("R",extra_path = "Emergence_yr"))

@@

Paths <- paste(my_path("R",extra_path = "Emergence_yr"),Taxon_List,"_emergence.txt",sep="")

# Load all sp in noe table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  )
# warnings() for empty data species

@@

# Per Stock
stock_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,taxon_key) %>%
  # summarise(n_tax = length(unique(eez_name))) %>%
  summarise(n()) %>% 
  mutate(
    level = "stock"
  ) %>% 
  select(1,3,4)
  # ggplot() +
  # geom_histogram(
  #   aes(
  #     x = emerging_yr
  #   ),
  #   stat = "count"
  # )

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,eez_name) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  select(1,3,4)

hist_data <- stock_d_hist %>% 
  bind_rows(eez_d_hist)

ggplot() +
  geom_density(data = subset(hist_data, level == "EEZ"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
  geom_density(data = subset(hist_data, level == "stock"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
    scale_y_continuous("Frequency",
                       breaks = seq(0,90,10),
                       limits = c(0,100)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T)

@@

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  ) %>% 
    select(1,3,4)

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(eez_name) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  ) %>% 
    select(1,3,4)

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d)

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    # Comment out for option A (Change plot name!!)
    geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
    geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,500,50),
                       limits = c(0,500)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  ggsave("./Figures/figure_accumulative_curve_B.png",
         width = 6,
         height = 6,
         units = "in"
  )
```
